NGO analysis

### 2022-07-21 Shiny/Test/Flexdashboard rows.Rmd
Creating KPIs private donations, public grants.

### KPI 4
```{r}
valueBoxOutput("KPI_box4")
```

@@

  # Creating the value box for administrative expenses
  output$KPI_box_admin <- renderValueBox({
    valueBox(
      value = KPI_to_string(KPI_admin_num()),
      caption = "Administration as a % of total expenses",
      color = met.brewer("Wissing", n = 1),
      icon = "fa-random"
    )
  })

@@

  # KPI_OPX
  output$KPI_box_OPX <- renderValueBox({
    valueBox(
      value = str_c(format(KPI_OPX_num(), digits = 3), "%"),
      caption = "Liquid assets / obligations",
      color = ifelse(KPI_OPX_num() <= 100, "success", "danger"),
      icon = "fas fa-coffee"
    )
  })

  # Duplicate value boxes for testing

  output$KPI_box4 <- renderValueBox({
    valueBox(
      value = KPI_to_string(KPI_admin_num()),
      caption = "Administration as a % of total expenses",
      color = met.brewer("Wissing", n = 1),
      icon = "fa-random"
    )
  })

  output$KPI_box5 <- renderValueBox({
    valueBox(
      value = KPI_to_string(KPI_admin_num()),
      caption = "Administration as a % of total expenses",
      color = met.brewer("Wissing", n = 1),
      icon = "fa-random"
    )
  })

  #---- Plots --------------------------------------------------------------------    
  #----CEO compensation-----------------------------------------------------------
  CEO_plot <- reactive({
    htmldata() |>
      # preparing for pivoting
      select(
        year, lederlonn, leder_annen_godtgjorelse
      ) |>
      # Compensation in ordinary numbers
      mutate(
        lederlonn = lederlonn * 1000,
        leder_annen_godtgjorelse = leder_annen_godtgjorelse * 1000
      ) |>
      # renaming for the purposes of the plot
      rename(
        Year = year,
        Salary = lederlonn,
        `Other compensation` = leder_annen_godtgjorelse
      ) |>
      # pivoting to join the two values to use fill
      pivot_longer(c(Salary, `Other compensation`), names_to = "Compensation") |>
      ggplot(aes(Year, value, fill = Compensation)) +
      geom_col() +
      currency_scale() +
      # pretty colours
      scale_fill_met_d("Troy") +
      labs(
        x = "", y = "Total compensation", title = "CEO compensation"
      )
  })

@@

  #----Expenses---------------------------------------
  expenses_plot <- reactive({
    exceldata() |>
      # Renaming for the purposes of the plot + dropping other variables
      transmute(
        Year = as.factor(year),
        Other = expenses_other,
        Administrative = expenses_administrative,
        Fundraising = expenses_fundraising,
        `Program services` = expenses_program_services
      ) |>
      # Pivoting to use fill
      pivot_longer(c(Other:`Program services`), names_to = "Expenses") |>
      ggplot(aes(Year, value, fill = Expenses)) +
      geom_col() +
      # Flipping, because the Excel file only contains two years atm
      coord_flip() +
      currency_scale() +
      scale_fill_met_d("Troy") +
      labs(x = "", y = "", title = "Expenses (in thousands)")
  })

@@

  # Reactive function with slightly nicer colours + ensuring positive values are always green
  scale_fill_green <- reactive({
    scale_fill_met_d("Tsimshian",
      direction = ifelse(
        mean(htmldata()$balance_positive,
          na.rm = TRUE
        ) == 1, -1, 1
      )
    )
  })
})

>>>>

### KPI 4
```{r}
valueBoxOutput("KPI_box_private")
```

@@

  # Creating private donations growth
  KPI_private_num <- reactive({
    exceldata() |>
      transmute(
        growth = revenue_private_contributions[1] / revenue_private_contributions[2] * 100
      ) |>
      pull() |>
      first()
  })

  # Creating public grants growth
  KPI_public_num <- reactive({
    exceldata() |>
      transmute(
        growth = revenue_public_grants[1] / revenue_public_grants[2] * 100
      ) |>
      pull() |>
      first()
  })

  # Creating the value box for administrative expenses
  output$KPI_box_admin <- renderValueBox({
    valueBox(
      value = KPI_to_string(KPI_admin_num()),
      caption = "Administration as a % of total expenses",
      color = "primary",
      icon = "fa-random"
    )
  })

@@

  # KPI_OPX
  output$KPI_box_OPX <- renderValueBox({
    valueBox(
      value = str_c(format(KPI_OPX_num(), digits = 3), "%"),
      caption = "Liquid assets / obligations",
      color = ifelse(KPI_OPX_num() <= 100, "success", "danger"),
      icon = "fas fa-seedling"
    )
  })

  # Creating value box for public grants growth
  output$KPI_box_private <- renderValueBox({
    valueBox(
      value = KPI_to_string(KPI_private_num()),
      caption = "Private donation growth",
      color = ifelse(KPI_private_num() < 100, "warning", "success"),
      icon = "fas fa-hands-helping"
    )
  })

  output$KPI_box5 <- renderValueBox({
    valueBox(
      value = KPI_to_string(KPI_public_num()),
      caption = "Public grants growth",
      color = ifelse(KPI_public_num() < 100, "warning", "success"),
      icon = "fas fa-hand-holding-usd"
    )
  })

  #---- Plots --------------------------------------------------------------------    
  #----CEO compensation-----------------------------------------------------------
  CEO_plot <- reactive({
    htmldata() |>
      # preparing for pivoting
      select(
        year, lederlonn, leder_annen_godtgjorelse
      ) |>
      # Compensation in ordinary numbers
      mutate(
        lederlonn = lederlonn * 1000,
        leder_annen_godtgjorelse = leder_annen_godtgjorelse * 1000
      ) |>
      # renaming for the purposes of the plot
      rename(
        Year = year,
        Salary = lederlonn,
        `Other compensation` = leder_annen_godtgjorelse
      ) |>
      # pivoting to join the two values to use fill
      pivot_longer(c(Salary, `Other compensation`), names_to = "Compensation") |>
      ggplot(aes(Year, value, fill = Compensation)) +
      geom_col() +
      currency_scale() +
      # pretty colours
      scale_fill_met_d("Hokusai2", direction = -1) +
      labs(
        x = "", y = "Total compensation", title = "CEO compensation"
      )
  })

@@

  #----Expenses---------------------------------------
  expenses_plot <- reactive({
    exceldata() |>
      # Renaming for the purposes of the plot + dropping other variables
      transmute(
        Year = as.factor(year),
        Other = expenses_other,
        Administrative = expenses_administrative,
        Fundraising = expenses_fundraising,
        `Program services` = expenses_program_services
      ) |>
      # Pivoting to use fill
      pivot_longer(c(Other:`Program services`), names_to = "Expenses") |>
      # Ordering for the plot
      mutate(
        Expenses = ordered(Expenses,
          levels =
            c("Program services", "Other", "Fundraising", "Administrative")
        )
      ) |>
      ggplot(aes(Year, value, fill = Expenses)) +
      geom_col() +
      # Flipping, because the Excel file only contains two years atm
      coord_flip() +
      currency_scale() +
      scale_fill_met_d("Hokusai2", direction = -1) +
      labs(x = "", y = "", title = "Expenses (in thousands)")
  })

@@

  # Reactive function with slightly nicer colours + ensuring positive values are
  # always green
  scale_fill_green <- reactive({
    scale_fill_met_d("Tsimshian",
      direction = ifelse(
        mean(htmldata()$balance_positive,
          na.rm = TRUE
        ) == 1, -1, 1
      )
    )
  })
})
